---
title: "Exp 1 - rope video"
date: "08/02/2021"
output:
  html_document: default
  pdf_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list = ls())

library(tidyverse)
library(summarytools)
library(exactRankTests)
library(lme4)
library(naniar)
library(gazer)
library(zoo)

##GAMM
library(itsadug)
packageVersion("itsadug")
library(plotfunctions)
packageVersion("plotfunctions")
library(colorspace)
packageVersion("colorspace")
## Define colors:
col1 <- 'pink1'
col2 <- 'black'
col3 <- 'indianred'
library(cowplot)

#load("reversed_videos_rope_gamm_workspace.RData")
```


###Loading data
```{r}
sample.data<-read.csv(file = "data/reversed_videos_sample_data_anonymised.csv")%>%
  filter(object== "rope")

table(sample.data$subject, sample.data$condition_trial)
table(sample.data$subject, sample.data$session)
table(sample.data$subject, sample.data$trial)
table(sample.data$subject, sample.data$object)
```

```{r}
## time.frame for interpolation
max.time <- 3000
min.time <- 0
time.frame <- seq(from = min.time, to = max.time, by = 1)
xx <- as.data.frame(time.frame)

baseline.end<-200
```



#### Artefact check
*Plot raw data
```{r}
raw.pupil_trial4<-ggplot(data = sample.data, aes(x = time.frame, y = RIGHT_PUPIL_SIZE)) +
  ylab("Pupil size") +
  xlab("Time (in ms)") +
  geom_point(aes(color = condition), alpha = 0.3, size = 0.5) +
  facet_grid(trial~subject)+
  xlim(min.time, max.time) +
    theme_bw()+
  scale_color_manual(values=c("darkorange", "dodgerblue"))+
  scale_fill_manual(values=c("darkorange", "dodgerblue"))+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.title = element_blank(), legend.position = "none", legend.text=element_text(size=12))

raw.pupil_trial4

ggsave(raw.pupil_trial4, filename = "graphics/reversed_videos_rope_pupil_size_raw.png", width=20, height = 8, scale = 0.8)
```
* Plot with blink artefacts removed
```{r}
sample.data<-sample.data%>%
        mutate(RIGHT_PUPIL_SIZE_no_blinks=extend_blinks(RIGHT_PUPIL_SIZE,  hz=1000, fillback=100, fillforward=100), RIGHT_GAZE_X_no_blinks=extend_blinks(RIGHT_GAZE_X,  hz=1000, fillback=100, fillforward=100), RIGHT_GAZE_Y_no_blinks=extend_blinks(RIGHT_GAZE_Y,  hz=1000, fillback=100, fillforward=100))#Extends blinks
```


```{r}
artefact_check_t4<-ggplot(data = sample.data, aes(x = time.frame, y = RIGHT_PUPIL_SIZE_no_blinks)) +
  ylab("Pupil size") +
  xlab("Time (in ms)") +
  geom_point(aes(color = condition), alpha = 0.1, size = 0.5) +
   facet_grid(trial~subject)+
 xlim(min.time, max.time) +
    theme_bw()+
  scale_color_manual(values=c("darkorange", "dodgerblue"))+
  scale_fill_manual(values=c("darkorange", "dodgerblue"))+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.title = element_blank(), legend.position = "none", legend.text=element_text(size=12))

#artefact_check_t4

ggsave(artefact_check_t4, filename = "graphics/reversed_videos_rope_artefact_check_rope.png", width=20, height=8)
```




* Plot distribution of pupil sizes
```{r eval=FALSE}
puphist <- ggplot(sample.data, aes(x = RIGHT_PUPIL_SIZE_no_blinks)) + geom_histogram(aes(y = ..count..), 
    colour = "green", binwidth = 0.5)  + 
    xlab("Pupil Size") + ylab("Count") + theme_bw() 
puphist
```

#### Preprocessing: interpolation, baseline correction, down sampling
```{r}
# subtractive baseline correction
exp.data.pupil.base <- sample.data %>%
  filter(time.frame < baseline.end & time.frame > 0) %>%
    group_by(subject, condition_trial) %>%
  summarise(median.base.pupil = median(RIGHT_PUPIL_SIZE_no_blinks, na.rm = TRUE))


exp.data.pupil.processed <- sample.data %>%
  filter(time.frame < max.time) %>% 
  select(subject, sex, time.frame, condition,  trial, condition_trial, RIGHT_GAZE_X_no_blinks, RIGHT_GAZE_Y_no_blinks, RIGHT_PUPIL_SIZE_no_blinks) %>%
  group_by(subject, sex, condition_trial, time.frame) %>%
  full_join(xx%>%select(time.frame)) %>% #add missing time.frames
  ungroup() %>%
  group_by(subject, sex, condition_trial) %>%
  mutate(pupil.inter = na.approx(RIGHT_PUPIL_SIZE_no_blinks, na.rm = FALSE, maxgap = 500)) %>% #linear interpolation
  full_join(exp.data.pupil.base) %>% #add baseline data
  mutate(pupil.base.corrected = pupil.inter - median.base.pupil)%>% #subtractive baseline correction
  ungroup()%>%
    mutate(bin = cut(time.frame, seq(min(time.frame), max(time.frame), 100), right = FALSE))%>% #addition of time bins (100 ms = 10 hz)
  separate(bin, c("bin_low", "bin_high"), sep=",", remove=FALSE)%>%
  select(-bin_high)%>%
  mutate(bin_low=as.numeric(str_replace_all(bin_low, "\\[|\\]", "")))
  
exp.data.pupil.processed.downsampled <- exp.data.pupil.processed %>%  
  group_by(subject, sex, condition,  condition_trial,trial, bin_low)%>%
  summarise(pupil.base.corrected.binned=median(pupil.base.corrected), Xgaze=mean(RIGHT_GAZE_X_no_blinks), Ygaze=mean(RIGHT_GAZE_Y_no_blinks)) #down sampling to 10hz using median values
```


* Plot interpolated data
```{r}
plot_individual_interpolated<-ggplot(data = exp.data.pupil.processed.downsampled%>%filter(!is.na(subject) & !is.na(trial)), aes(x = bin_low, y =pupil.base.corrected.binned )) +
  ylab("Pupil size") +
  xlab("Time (in ms)") +
  geom_point(aes(color = condition), alpha = 0.8, size = 0.5) +
 facet_grid(trial~subject)+
  xlim(min.time, max.time) +
    theme_bw()+
  scale_color_manual(values=c("darkorange", "dodgerblue"))+
  scale_fill_manual(values=c("darkorange", "dodgerblue"))+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.title = element_blank(), legend.position = "none",#c(0.85, 0.8),
        legend.text=element_text(size=12))

plot_individual_interpolated

ggsave(plot_individual_interpolated, filename = "graphics/reversed_videos_rope_pupil_size_individual_interpolated.png", width=24, height=8)

```

* Plot group level data
```{r}
exp.data.pupil.processed.downsampled$condition<-relevel(as.factor(exp.data.pupil.processed.downsampled$condition), "normal", "reversed")

pupil.group.level <- exp.data.pupil.processed.downsampled %>%
    mutate(condition=as.factor(condition))%>%
  group_by(bin_low, condition) %>%
  summarise(mean.pupil.corrected.binned = mean(pupil.base.corrected.binned, na.rm = TRUE), sd.pupil.corrected.binned= sd(pupil.base.corrected.binned, na.rm = TRUE), se.pupil.corrected.binned = sd(pupil.base.corrected.binned, na.rm = TRUE) / sqrt(length(pupil.base.corrected.binned)))%>%
  mutate(condition=fct_recode(condition, "Normal"="normal", "Reversed"="reversed"))%>%
  droplevels()

plot.reversed_videos_rope.pupil <- ggplot(data = pupil.group.level%>%filter(!is.na(condition)), aes(x = bin_low, y = mean.pupil.corrected.binned)) +
  ylab("Pupil size") +
  xlab("Time (in ms)") +
#   geom_vline(aes(xintercept=4000), lty=1, col="darkgrey")+
 #  geom_vline(aes(xintercept=5000), lty=2, col="darkgrey")+
  geom_path(aes(x = bin_low, y = mean.pupil.corrected.binned, color = condition), alpha = 0.6, size = 0.6) +
  geom_ribbon(aes(ymin = mean.pupil.corrected.binned - se.pupil.corrected.binned, ymax = mean.pupil.corrected.binned + se.pupil.corrected.binned, fill = condition), alpha = 0.4) +
    xlim(min.time, max.time) +
    theme_bw()+
  scale_color_manual(values=c("darkorange", "dodgerblue"))+
  scale_fill_manual(values=c("darkorange", "dodgerblue"))+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.title = element_blank(), legend.position = c(0.2, 0.8), legend.text=element_text(size=12))


plot.reversed_videos_rope.pupil

ggsave(plot.reversed_videos_rope.pupil, filename = "graphics/reversed_videos_rope_pupil_base_corrected.png", height = 6, width = 8, scale = 0.6)
```


* Plot group level data by trial number
```{r}

pupil.group.level.trial <- exp.data.pupil.processed.downsampled %>%
  mutate(condition=as.factor(condition))%>%
  group_by(bin_low, condition, trial) %>%
  summarise(mean.pupil.corrected.binned = mean(pupil.base.corrected.binned, na.rm = TRUE), sd.pupil.corrected.binned= sd(pupil.base.corrected.binned, na.rm = TRUE), se.pupil.corrected.binned = sd(pupil.base.corrected.binned, na.rm = TRUE) / sqrt(length(pupil.base.corrected.binned)))%>%
  mutate(condition=fct_recode(condition, "Normal"="normal", "Reversed"="reversed"))%>%
  droplevels()

plot.reversed_videos_rope.pupil.trial1 <- ggplot(data = pupil.group.level.trial%>%filter(!is.na(condition), trial==5), aes(x = bin_low, y = mean.pupil.corrected.binned)) +
  ylab("Pupil size") +
  xlab("Time (in ms)") +
  #geom_vline(aes(xintercept=4000), lty=1, col="darkgrey")+
   #geom_vline(aes(xintercept=5000), lty=2, col="darkgrey")+
      geom_path(aes(x = bin_low, y = mean.pupil.corrected.binned, color = condition), alpha = 0.5, size = 0.5) +
  geom_ribbon(aes(ymin = mean.pupil.corrected.binned - se.pupil.corrected.binned, ymax = mean.pupil.corrected.binned + se.pupil.corrected.binned, fill = condition), alpha = 0.5) +
    xlim(min.time, max.time) +
    theme_bw()+
  scale_color_manual(values=c("darkorange", "dodgerblue"))+
  scale_fill_manual(values=c("darkorange", "dodgerblue"))+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.title = element_blank(), legend.position = c(0.8, 0.12), legend.text=element_text(size=12))


plot.reversed_videos_rope.pupil.trial1

ggsave(plot.reversed_videos_rope.pupil.trial1, filename = "graphics/reversed_videos_rope_pupil_base_corrected_trial1.png", height = 6, width = 8, scale = 0.6)
```

```{r}
save.image(file = "reversed_videos_rope_gamm_workspace.RData")
```


### GAMM
`
* Plot gaze positions
```{r}
emptyPlot(c(0,1024), c(768, 0), bty='o',
          main="Gaze positions", xlab="Xgaze", ylab="Ygaze")
points(exp.data.pupil.processed.downsampled$Xgaze, exp.data.pupil.processed.downsampled$Ygaze, pch=16, cex=.5, col=alpha(1), xpd=TRUE)
abline(h=768/2, v=1024/2, lty=1, col='white')
abline(h=768/2, v=1024/2, lty=2, col=1)
```

* Plot pupil size by subject
```{r}
par(cex=1.1)
bp <- sortBoxplot(exp.data.pupil.processed.downsampled$pupil.base.corrected.binned ~ exp.data.pupil.processed.downsampled$subject, col=alpha(1), decreasing=FALSE,
                  ylab="Pupil size", xlab="Subject", bty='n', pch=".")


```

#### data preparation for GAMM

* select interest period
```{r}
dat <- exp.data.pupil.processed.downsampled%>%
  filter(bin_low >= baseline.end & bin_low <= (max.time))%>% #select interest period
  rename(pupil_base="pupil.base.corrected.binned", time="bin_low")%>%
  arrange(subject, condition, trial, time)%>%#order dataframe
  droplevels()
dat$condition<-as.factor(dat$condition)
dat$subject<-as.factor(dat$subject)
```

#### taking autocorrelation into account

```{r}
# Defining events (time series):
dat$Event <- interaction(dat$subject, dat$condition_trial, drop=TRUE)

m2 <- bam(pupil_base ~ condition + s(time, k=20)+ s(time, by=condition, k=20) 
          + s(Xgaze, Ygaze)
          + s(time, Event, bs='fs', m=1)
          , data=dat, discrete=TRUE, nthreads=40, method="ML")


m2.null <- bam(pupil_base ~ s(time, k=20)+ 
          + s(Xgaze, Ygaze)
          + s(time, Event, bs='fs', m=1)
          , data=dat, discrete=TRUE, nthreads=40, method="ML")

save.image(file = "reversed_videos_rope_gamm_workspace.RData")
```


```{r}
summary(m2)

gam.check(m2)
acf(resid(m2), bty='n', main="ACF residuals model1")
acf(resid(m2), plot=FALSE)

compareML(m2, m2.null)
AIC(m2, m2.null)

```



* difference curve
```{r}

plot_diff(m2, view="time", 
          comp=list(condition=c("normal", "reversed")), rm.ranef=TRUE, main="Normal - Reversed", 
          las=1, ylab="Est. difference in pupil size", 
            col=col2, hide.label = TRUE, plot = TRUE)#col.diff=alpha(1,f=0),v0=1800,

plot_diff_no_plot<-plot_diff(m2, view="time", 
          comp=list(condition=c("normal", "reversed")), rm.ranef=TRUE, main="Normal - Reversed", 
          las=1, ylab="Est. difference in pupil size", 
            col=col2, hide.label = TRUE, plot = FALSE)

plot_diff_m2_gg<-ggplot(data=plot_diff_no_plot, aes(x=time, y=est))+
  geom_hline(yintercept = 0)+
  geom_path(lty=2)+
  geom_ribbon(aes(x=time, ymin=est-CI, ymax=est+CI), alpha=0.2)+
  theme_bw()+
  scale_x_continuous(name="Time (in ms)", breaks=c(1000, 2000, 3000, 4000, 5000))+ ylab("Est. difference in pupil size")+ggtitle("Normal - Reversed")+
    theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

ggsave(plot_diff_m2_gg, filename = "graphics/plot_reversed_videos_rope_m2_diffcurve.png", width=6, height=5, scale=0.6)
```

```{r}
library(cowplot)
pg.1<-cowplot::plot_grid(plot.reversed_videos_rope.pupil,plot_diff_m2_gg, nrow=1,ncol=2, rel.width=c(2.5,1, 0),labels = c("D", "E"))
```

* plotting partial effects
```{r}
png("graphics/plot_reversed_videos_rope_m2_paterial_effect.png", width=20, height=16, units="cm", res=300)
plot(m2, pages = 1, all.terms = TRUE, residuals = TRUE, rug=FALSE, pch = 1, cex = 0.5, seWithMean = TRUE, shade = TRUE, shade.col = "lightblue")
dev.off()

library(mgcViz)
b <- getViz(m2)
png("graphics/plot_reversed_videos_rope_m2_paterial_effect2.png", width=20, height=16, units="cm", res=300)
p1<-plot(b, allTerms = T)+theme_classic() + labs(title = NULL)
print(p1, pages = 1 )
dev.off()

```


* Summed effects
```{r}

plot_smooth(m2, view="time", cond=list(condition="normal"), rm.ranef=TRUE,
  v0=0, col=col2, lwd=2, lty=6, rug=FALSE, se=1.96,
  main="Estimated effects", ylab="Pupil (baselined)", las=1,
  ylim=c(-1000,1000))

plot_smooth(m2, view="time", cond=list(condition="reversed"), rm.ranef=TRUE,
  v0=0, col=col2, lwd=2, lty=6, rug=FALSE, se=1.96,
  main="Estimated effects", ylab="Pupil (baselined)", las=1,
  ylim=c(-1000,1000))


```

```{r}

tmp <- m2$model

plot_modelfit(m2, view="time", event=tmp$Event,n = 5)

```

### Plot gaze data: rope
Interpolate AI values

```{r}
ai.data <- read_delim(file="data/reversed_videos_rope_dynamic_IA.txt", delim="\t") %>%
  mutate(x_average = (x_l + x_r)/2, y_average = (y_up + y_low)/2, time.frame = start)

ai.data.normal<-ai.data%>% filter(label=="rope_IA_normal")
ai.data.reversed<-ai.data%>% filter(label=="rope_IA_reversed")

## interpolation
max.time2 <- max(ai.data.normal$end)
min.time2 <- min(ai.data.normal$start)
time.frame <- seq(from = min.time2, to = max.time2, by = 1)
xx <- as.data.frame(time.frame)
library(zoo)

rope.normal.data <- xx %>%
  full_join(ai.data.normal, by = "time.frame") %>%
  mutate(x_approx = na.approx(x_average), x_l_approx = na.approx(x_l), x_r_approx = na.approx(x_r), y_approx = na.approx(y_average), y_up_approx = na.approx(y_up), y_low_approx = na.approx(y_low))

## interpolation
max.time2 <- max(ai.data.reversed$end)
min.time2 <- min(ai.data.reversed$start)
time.frame <- seq(from = min.time2, to = max.time2, by = 1)
xx <- as.data.frame(time.frame)

rope.reversed.data <- xx %>%
  full_join(ai.data.reversed, by = "time.frame") %>%
  mutate(x_approx = na.approx(x_average), x_l_approx = na.approx(x_l), x_r_approx = na.approx(x_r), y_approx = na.approx(y_average), y_up_approx = na.approx(y_up), y_low_approx = na.approx(y_low))

```

* plot vertical gaze
```{r}
gaze_plot_data <- exp.data.pupil.processed.downsampled %>%
  filter(bin_low < max.time ) %>%
  group_by(bin_low, condition) %>%
  summarise(mean.x = mean(Xgaze, na.rm=TRUE), median.x = median(Xgaze,  na.rm=TRUE), se.x = sd(Xgaze, na.rm=TRUE) / sqrt(length(Xgaze)), mean.y = mean(Ygaze, na.rm=TRUE), median.y = median(Ygaze,  na.rm=TRUE), se.y = sd(Ygaze, na.rm=TRUE) / sqrt(length(Ygaze))) %>%
  mutate(time.frame=bin_low)%>%
   left_join(rope.normal.data%>%select(time.frame, x_l_approx, x_r_approx, x_approx, y_up_approx, y_low_approx, y_approx)%>%rename(x_l_normal=x_l_approx, x_r_normal=x_r_approx, x_normal=x_approx, y_up_normal=y_up_approx, y_low_normal=y_low_approx, y_normal=y_approx))%>%
        left_join(rope.reversed.data%>%select(time.frame, x_l_approx, x_r_approx, x_approx, y_up_approx, y_low_approx, y_approx)%>%rename(x_l_reversed=x_l_approx, x_r_reversed=x_r_approx, x_reversed=x_approx, , y_up_reversed=y_up_approx, y_low_reversed=y_low_approx, y_reversed=y_approx))
```

```{r}

con.labs <- c("Normal", "Reversed")
names(con.labs) <- c(levels(as.factor(gaze_plot_data$condition)))



plot_reversed_videos_rope_gaze_vertical<-ggplot(data = gaze_plot_data%>%filter(!is.na(condition)), aes(x = time.frame, y = mean.y)) +
      facet_wrap(~condition,labeller=labeller(condition=con.labs)) +
  #moving rope:
  geom_ribbon(data = gaze_plot_data %>% filter(condition=="reversed"), aes(x = time.frame, ymin = y_up_reversed, ymax = y_low_reversed), fill = "darkgoldenrod1", alpha = 0.8) +
    geom_ribbon(data = gaze_plot_data %>% filter(condition=="normal"), aes(x = time.frame, ymin = y_up_normal, ymax = y_low_normal), fill = "darkgoldenrod1", alpha = 0.8) +
# gaze data:
    geom_point(alpha = 0.1, size=0.5) +
  geom_path(aes(y = median.y), size = 1.2) +
   geom_ribbon(aes(ymin = mean.y - se.y, ymax = mean.y + se.y), alpha = 0.5)+
  ylab("Vertical coordinates (in px)") +
  xlab("Time (in ms)") +
  #ylim(-50, 1000)+
    theme_bw()+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        strip.text.x = element_text(size = 12))+
  scale_y_reverse()

plot_reversed_videos_rope_gaze_vertical
ggsave(plot_reversed_videos_rope_gaze_vertical,filename="graphics/plot_reversed_videos_rope_vertical_gaze.png", height = 5, width = 8, scale = 0.7)
```

### Adding screenshots: rope

```{r}
library(cowplot)

rope_reversed_ini_photo <- "screenshots/rope_reversed.mp4_snapshot_00.00.000.jpg"
rope_reversed_mid2_photo <- "screenshots/rope_reversed.mp4_snapshot_00.01.100.jpg"
rope_reversed_fin_photo <- "screenshots/rope_reversed.mp4_snapshot_00.02.034.jpg"


rope_reversed_ini_photo <- ggdraw(theme(plot.margin = unit(c(0, 0, 0, 0), "cm"))) + draw_image(rope_reversed_ini_photo)
rope_reversed_mid2_photo <- ggdraw(theme(plot.margin = unit(c(0, 0, 0,0), "cm"))) + draw_image(rope_reversed_mid2_photo)
rope_reversed_fin_photo <- ggdraw(theme(plot.margin = unit(c(0, 0, 0,0), "cm"))) + draw_image(rope_reversed_fin_photo)


rope_reversed_pics<-plot_grid(rope_reversed_fin_photo, rope_reversed_mid2_photo, rope_reversed_ini_photo, nrow=1)


```


### Dwell time
Read Data

```{r}
end.ip.data<-read.csv(file="data/reversed_videos_IA_report_rope_anonymised.csv")
```

```{r}
test.IP.end.IA.endpos <- end.ip.data %>%
  mutate(IA_LABEL2=ifelse(IA_LABEL=="Rope_low" & condition=="normal", "IA_end_position", ifelse(IA_LABEL=="Rope_up" & condition=="reversed", "IA_end_position", "")))%>%
  filter(IA_LABEL2=="IA_end_position")%>%
  group_by(subject, condition)%>%
  summarise(mean_dwell=mean(IA_DWELL_TIME))


t.test(test.IP.end.IA.endpos$mean_dwell[test.IP.end.IA.endpos$condition=="normal"], test.IP.end.IA.endpos$mean_dwell[test.IP.end.IA.endpos$condition=="reversed"], paired=TRUE)

```

```{r}

test.IP.end.IA.endpos$condition2 <- jitter(as.numeric(as.factor(test.IP.end.IA.endpos$condition), amount = .0001))
y_lim_min<-0
y_lim_max<-1100

library(gghalves)


plot_end_rope <- ggplot(data = test.IP.end.IA.endpos, aes(x = condition, y= mean_dwell)) +
  #Add geom_() objects
   geom_point(data = test.IP.end.IA.endpos %>% filter(condition =="normal"), aes(x = condition2), color = 'darkorange', size = 1.5, 
              alpha = .5) +
   geom_point(data = test.IP.end.IA.endpos %>% filter(condition =="reversed"), aes(x = condition2), color = 'dodgerblue', size = 1.5, 
              alpha = .5) +
   geom_line(aes(x = condition2, group = subject), color = 'lightgray', alpha = .5) +
  
   geom_half_boxplot(
     data = test.IP.end.IA.endpos %>% filter(condition=="normal"), aes(x=condition2, y = mean_dwell), position = position_nudge(x = -.4), 
     side = "r",outlier.shape = NA, center = TRUE, errorbar.draw = TRUE, width = .1, 
     fill = 'darkorange', alpha = .5) +
   
   geom_half_boxplot(
     data = test.IP.end.IA.endpos %>% filter(condition=="reversed"), aes(x=condition2, y = mean_dwell), position = position_nudge(x = .25), 
     side = "r",outlier.shape = NA, center = TRUE, errorbar.draw = TRUE, width = .1, 
     fill = 'dodgerblue', alpha = .5) +
    #Define additional settings
   scale_x_continuous(breaks=c(1,2), labels=c("Normal", "Reversed"), limits=c(0.4, 2.5)) +
   xlab("Condition") + ylab("Dwell time (in ms)") +
 #  ggtitle('Cube: end position') +
   theme_classic()+
   coord_cartesian(ylim=c(y_lim_min, y_lim_max))
  
plot_end_rope 
 
ggsave(plot_end_rope, filename = "graphics/plot_end_pos_rope.png", height=5, width=5, scale=0.8)
```


```{r}

pg.2<-plot_grid(plot_reversed_videos_rope_gaze_vertical, plot_end_rope,  ncol=2,nrow=1, rel_widths = c(2,1), labels = c("B","C") )

pg.reversed_video_rope.pics<-plot_grid(rope_reversed_pics, pg.2, pg.1, ncol=1, rel_heights = c(0.6,0.75 , 0.75), labels = c("A", "",""))

pg.reversed_video_rope.pics

ggsave(pg.reversed_video_rope.pics, filename = "graphics/pg_reversed_video_rope.png", width = 14, height=12, scale=0.8)

ggsave(pg.reversed_video_rope.pics, filename = "graphics/pg_reversed_video_rope.pdf", width = 14, height=12, scale=0.8)
```



## Dynamic AoI analysis: r-squared


```{r}
dynamic.aoi.data <- sample.data %>%
  filter(time.frame < 3000) %>%
  group_by(condition,subject, trial, time.frame) %>%
  summarise(mean.x = mean(RIGHT_GAZE_X_no_blinks), mean.y = mean(RIGHT_GAZE_Y)) %>%
   left_join(rope.normal.data%>%select(time.frame, x_l_approx, x_r_approx, x_approx, y_up_approx, y_low_approx, y_approx)%>%rename(x_l_normal=x_l_approx, x_r_normal=x_r_approx, x_normal=x_approx, y_up_normal=y_up_approx, y_low_normal=y_low_approx, y_normal=y_approx))%>%
        left_join(rope.reversed.data%>%select(time.frame, x_l_approx, x_r_approx, x_approx, y_up_approx, y_low_approx, y_approx)%>%rename(x_l_reversed=x_l_approx, x_r_reversed=x_r_approx, x_reversed=x_approx, , y_up_reversed=y_up_approx, y_low_reversed=y_low_approx, y_reversed=y_approx))


dynamic.aoi.data$condition<-as.factor(dynamic.aoi.data$condition)
levels(dynamic.aoi.data$condition)


```


```{r}
library(broom)

r2.normal <- dynamic.aoi.data %>%
  select(subject, condition,time.frame, trial, mean.y, y_normal)%>%
  filter(time.frame < 2000 & time.frame > 500 & (condition=="normal")) %>% 
  droplevels() %>%
  nest(-subject, -condition, -trial) %>%
  mutate(
    fit = map(data, ~ lm(mean.y ~ y_normal, data = .)),
    results = map(fit, glance)
  ) %>%
  unnest(results) %>%
  select(subject, condition, trial, r.squared) %>%
  rename(r.sq.exp = r.squared) %>%
  mutate(across(where(is.numeric), round, 3))

r2.reversed <- dynamic.aoi.data %>%
  select(subject, condition,time.frame, trial, mean.y, y_reversed)%>%
  filter(time.frame < 2000 & time.frame > 500 & (condition=="reversed")) %>% 
  droplevels() %>%
  nest(-subject, -condition, -trial) %>%
  mutate(
    fit = map(data, ~ lm(mean.y ~ y_reversed, data = .)),
    results = map(fit, glance)
  ) %>%
  unnest(results) %>%
  select(subject, condition, trial, r.squared) %>%
  rename(r.sq.exp = r.squared) %>%
  mutate(across(where(is.numeric), round, 3))

r2.normal %>%
  group_by(condition, subject) %>%
  summarise(r.sq.exp = mean(r.sq.exp))%>%
  group_by(condition) %>%
  summarise(mean = mean(r.sq.exp), median = median(r.sq.exp), min = min(r.sq.exp), max = max(r.sq.exp), sd = sd(r.sq.exp), se = sd(r.sq.exp)/length(r.sq.exp), n=length(r.sq.exp))

r2.reversed %>%
  group_by(condition, subject) %>%
  summarise(r.sq.exp = mean(r.sq.exp))%>%
  group_by(condition) %>%
  summarise(mean = mean(r.sq.exp), median = median(r.sq.exp), min = min(r.sq.exp), max = max(r.sq.exp), sd = sd(r.sq.exp), se = sd(r.sq.exp)/length(r.sq.exp), n=length(r.sq.exp))



```



## Trial report analysis

* Read Data
```{r}
trial.data<-read.csv(file="data/reversed_videos_Trial_report_rope_anonymised.csv")
```
* descriptives
```{r}
trial.data.ind<-trial.data%>%
  group_by(condition, subject)%>%
  summarise(fix_duration=mean(AVERAGE_FIXATION_DURATION), sacc_amplitude=mean(AVERAGE_SACCADE_AMPLITUDE), fix_count=mean(	FIXATION_COUNT), max_pupil_size=mean(PUPIL_SIZE_MAX), sacc_count=mean(SACCADE_COUNT))%>%
ungroup()

trial_descriptives<-trial.data.ind%>%
  group_by(condition)%>%
  summarise(mean_fix_duration=mean(fix_duration), se_fix_duration=sd(fix_duration)/length(fix_duration), mean_fix_count=mean(fix_count), se_fix_count=sd(fix_count)/length(fix_count), mean_sacc_amplitude=mean(sacc_amplitude), se_sacc_amplitude=sd(sacc_amplitude)/length(sacc_amplitude), mean_sacc_count=mean(sacc_count),se_sacc_count=sd(sacc_count)/length(sacc_count), n=length(sacc_count))

write.csv(trial_descriptives, file = "saves/trial_descriptives_rope.csv")

```

```{r}



library(broom)
x1<-trial.data.ind%>%
  summarise(ttest_fix_duration = list(t.test(fix_duration ~ condition, paired=TRUE)))%>%
  mutate(ttest_fix_duration = map(ttest_fix_duration, tidy)) %>%
  unnest()


x2<-trial.data.ind%>%
  summarise(ttest = list(t.test(fix_count ~ condition, paired=TRUE)))%>%
  mutate(ttest = map(ttest, tidy)) %>%
  unnest()

x3<-trial.data.ind%>%
  summarise(ttest = list(t.test(sacc_amplitude ~ condition, paired=TRUE)))%>%
  mutate(ttest = map(ttest, tidy)) %>%
  unnest()

x4<-trial.data.ind%>%
  summarise(ttest = list(t.test(sacc_count ~ condition, paired=TRUE)))%>%
  mutate(ttest = map(ttest, tidy)) %>%
  unnest()
rowname<-c("fix_duration", "fix_count", "sacc_amp", "sacc_count")
xx<-cbind(rowname,rbind(x1,x2, x3,x4))
write.csv(xx, file = "saves/trial_ttest_rope.csv")

```










