---
title: "Exp2 - analysis"
date: "01/07/2021"
output:
  html_document: default
  pdf_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list = ls())
library(tidyverse)
library(summarytools)
library(exactRankTests)
library(lme4)
library(naniar)
library(gazer)
library(zoo)
source("../../../../R scripts/Roger/diagnostic_fcns.r")
source("../../../../R scripts/Roger/glmm_stability.r")
source("../../../../R scripts/Roger/glmmTMB_stability.r")
source("../../../../R scripts/Roger/boot_glmm.r")
source("../../../../R scripts/Roger/drop1_para.r")

##GAMM
library(itsadug)
packageVersion("itsadug")
library(plotfunctions)
packageVersion("plotfunctions")
library(colorspace)
packageVersion("colorspace")
## Define colors:
col1 <- 'pink1'
col2 <- 'black'
col3 <- 'indianred'
library(cowplot)

#load("animacy_gamm_workspace3.RData")
```


### Download sample report (>100MB)
```{r eval=FALSE}
library(piggyback)
pb_download("variable_motion_sample_data_anonymised.csv", repo = "cvoelter/dog_animacy_perception", dest = "./data")
```



### Loading data

```{r}
sample.data<-read.csv(file = "data/variable_motion_sample_data_anonymised.csv")
```

## Pupil size preprocessing

```{r}
## time.frame for interpolation
max.time <- 20000
min.time <- 0
time.frame <- seq(from = min.time, to = max.time, by = 1)
xx <- as.data.frame(time.frame)

baseline.end<-1000
```

*Plot raw data
```{r}
raw.pupil_trial4<-ggplot(data = sample.data, aes(x = time.frame, y = RIGHT_PUPIL_SIZE)) +
  ylab("Pupil size") +
  xlab("Time (in ms)") +
  geom_point(aes(color = condition), alpha = 0.3, size = 0.5) +
  facet_grid(trial~subject)+
  xlim(0, 20000) +
    theme_bw()+
  scale_color_manual(values=c("darkorange", "dodgerblue", "darkgreen", "yellow"))+
  scale_fill_manual(values=c("darkorange", "dodgerblue",  "darkgreen", "yellow"))+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.title = element_blank(), legend.position = "none", legend.text=element_text(size=12))

raw.pupil_trial4

ggsave(raw.pupil_trial4, filename = "graphics/Exp2_pupil_size_raw.png", width=20, height = 8, scale = 0.8)
```
* Plot with blink artefacts removed
```{r}
sample.data<-sample.data%>%
        mutate(RIGHT_PUPIL_SIZE_no_blinks=extend_blinks(RIGHT_PUPIL_SIZE,  hz=1000, fillback=100, fillforward=100), RIGHT_GAZE_X_no_blinks=extend_blinks(RIGHT_GAZE_X,  hz=1000, fillback=100, fillforward=100), RIGHT_GAZE_Y_no_blinks=extend_blinks(RIGHT_GAZE_Y,  hz=1000, fillback=100, fillforward=100))#Extends blinks
```


```{r}
artefact_check_t4<-ggplot(data = sample.data, aes(x = time.frame, y = RIGHT_PUPIL_SIZE_no_blinks)) +
  ylab("Pupil size") +
  xlab("Time (in ms)") +
  geom_point(aes(color = condition), alpha = 0.1, size = 0.5) +
   facet_grid(trial~subject)+
  xlim(0, 20000) +
    theme_bw()+
  scale_color_manual(values=c("darkorange", "dodgerblue", "darkgreen", "yellow"))+
  scale_fill_manual(values=c("darkorange", "dodgerblue",  "darkgreen", "yellow"))+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.title = element_blank(), legend.position = "none", legend.text=element_text(size=12))

#artefact_check_t4

ggsave(artefact_check_t4, filename = "graphics/Exp2_contact_artefact_check.png", width=20, height=8)
```


* Plot distribution of pupil sizes
```{r eval=FALSE}
puphist <- ggplot(sample.data, aes(x = RIGHT_PUPIL_SIZE_no_blinks)) + geom_histogram(aes(y = ..count..), 
    colour = "green", binwidth = 0.5)  + 
    xlab("Pupil Size") + ylab("Count") + theme_bw() 
puphist
```

### Preprocessing: interpolation, baseline correction, down sampling
```{r}
# subtractive baseline correction
exp.data.pupil.base <- sample.data %>%
  filter(time.frame < baseline.end & time.frame > 0) %>%
    group_by(subject, condition_trial) %>%
  summarise(median.base.pupil = median(RIGHT_PUPIL_SIZE_no_blinks, na.rm = TRUE))


exp.data.pupil.processed <- sample.data %>%
  filter(time.frame < max.time) %>% 
  select(subject, sex, time.frame, condition, stimulus, motion, trial, condition_trial, RIGHT_GAZE_X_no_blinks, RIGHT_GAZE_Y_no_blinks, RIGHT_PUPIL_SIZE_no_blinks) %>%
  group_by(subject, sex, condition_trial, time.frame) %>%
  full_join(xx%>%select(time.frame)) %>% #add missing time.frames
  ungroup() %>%
  group_by(subject, sex, condition_trial) %>%
  mutate(pupil.inter = na.approx(RIGHT_PUPIL_SIZE_no_blinks, na.rm = FALSE, maxgap = 500)) %>% #linear interpolation
  full_join(exp.data.pupil.base) %>% #add baseline data
  mutate(pupil.base.corrected = pupil.inter - median.base.pupil)%>% #subtractive baseline correction
  ungroup()%>%
    mutate(bin = cut(time.frame, seq(min(time.frame), max(time.frame), 100), right = FALSE))%>% #addition of time bins (100 ms = 10 hz)
  separate(bin, c("bin_low", "bin_high"), sep=",", remove=FALSE)%>%
  select(-bin_high)%>%
  mutate(bin_low=as.numeric(str_replace_all(bin_low, "\\[|\\]", "")))
  
exp.data.pupil.processed.downsampled <- exp.data.pupil.processed %>%  
  group_by(subject, sex, condition, stimulus, motion, condition_trial,trial, bin_low)%>%
  summarise(pupil.base.corrected.binned=median(pupil.base.corrected), Xgaze=mean(RIGHT_GAZE_X_no_blinks), Ygaze=mean(RIGHT_GAZE_Y_no_blinks)) #down sampling to 10hz using median values
```


* Plot interpolated data
```{r}
plot_individual_interpolated<-ggplot(data = exp.data.pupil.processed.downsampled%>%filter(!is.na(subject) & !is.na(trial)), aes(x = bin_low, y =pupil.base.corrected.binned )) +
  ylab("Pupil size") +
  xlab("Time (in ms)") +
  geom_point(aes(color = condition), alpha = 0.8, size = 0.5) +
 facet_grid(trial~subject)+
  xlim(0, 20000) +
    theme_bw()+
  scale_color_manual(values=c("darkorange", "dodgerblue", "darkgreen", "yellow"))+
  scale_fill_manual(values=c("darkorange", "dodgerblue",  "darkgreen", "yellow"))+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.title = element_blank(), legend.position = "none",#c(0.85, 0.8),
        legend.text=element_text(size=12))

plot_individual_interpolated

ggsave(plot_individual_interpolated, filename = "graphics/Exp2_pupil_size_individual_interpolated.png", width=24, height=8)

```

* Plot group level data
```{r}
exp.data.pupil.processed.downsampled$condition<-relevel(as.factor(exp.data.pupil.processed.downsampled$condition), "B-C", "B-V", "F-C", "F-V")

pupil.group.level <- exp.data.pupil.processed.downsampled %>%
    mutate(condition=as.factor(condition), stimulus=as.factor(stimulus), motion=as.factor(motion))%>%
  group_by(bin_low, condition, stimulus, motion) %>%
  summarise(mean.pupil.corrected.binned = mean(pupil.base.corrected.binned, na.rm = TRUE), sd.pupil.corrected.binned= sd(pupil.base.corrected.binned, na.rm = TRUE), se.pupil.corrected.binned = sd(pupil.base.corrected.binned, na.rm = TRUE) / sqrt(length(pupil.base.corrected.binned)))%>%
  mutate(condition=fct_recode(condition, "Ball-constant"="B-C", "Ball-variable"="B-V", "Fur-constant"="F-C", "Fur-variable"="F-V"))%>%
    mutate(motion=fct_recode(motion, "Constant"="C", "Variable"="V"), stimulus=fct_recode(stimulus, "Fur"="F", "Ball"="B"))%>%
  droplevels()

plot.animacy.pupil <- ggplot(data = pupil.group.level%>%filter(!is.na(condition)), aes(x = bin_low, y = mean.pupil.corrected.binned)) +
  facet_wrap(~stimulus)+
  ylab("Pupil size") +
  xlab("Time (in ms)") +
   geom_vline(aes(xintercept=4000), lty=1, col="darkgrey")+
   geom_vline(aes(xintercept=5000), lty=2, col="darkgrey", alpha=0.5)+
     geom_vline(aes(xintercept=6000), lty=2, col="darkgrey", alpha=0.5)+
     geom_vline(aes(xintercept=12320), lty=2, col="darkgrey", alpha=0.5)+
     geom_vline(aes(xintercept=12740), lty=2, col="darkgrey", alpha=0.5)+
       geom_vline(aes(xintercept=13990), lty=2, col="darkgrey", alpha=0.5)+
     geom_vline(aes(xintercept=14600), lty=2, col="darkgrey", alpha=0.5)+
         geom_vline(aes(xintercept=8700), lty=2, col="darkgrey", alpha=0.5)+
     geom_vline(aes(xintercept=8870), lty=2, col="darkgrey", alpha=0.5)+
      geom_vline(aes(xintercept=8000), lty=1, col="darkgrey")+
    geom_vline(aes(xintercept=12000), lty=1, col="darkgrey")+
      geom_vline(aes(xintercept=16000), lty=1, col="darkgrey")+
  geom_path(aes(x = bin_low, y = mean.pupil.corrected.binned, color = motion), alpha = 0.6, size = 0.6) +
  geom_ribbon(aes(ymin = mean.pupil.corrected.binned - se.pupil.corrected.binned, ymax = mean.pupil.corrected.binned + se.pupil.corrected.binned, fill = motion), alpha = 0.4) +
    xlim(0, 19000) +
    theme_bw()+
  scale_color_manual(values=c("darkorange", "dodgerblue" ))+
  scale_fill_manual(values=c("darkorange", "dodgerblue" ))+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.title = element_blank(), legend.position = c(0.1, 0.85), legend.text=element_text(size=12),
        strip.text.x = element_text(size = 12))

plot.animacy.pupil

ggsave(plot.animacy.pupil, filename = "graphics/Exp2.pupil_baseline_corrected.png", height = 6, width = 14, scale = 0.6)
```


* Plot group level data by trial number
```{r}

pupil.group.level.trial <- exp.data.pupil.processed.downsampled %>%
  mutate(condition=as.factor(condition))%>%
  group_by(bin_low, condition, motion, stimulus, trial) %>%
  summarise(mean.pupil.corrected.binned = mean(pupil.base.corrected.binned, na.rm = TRUE), sd.pupil.corrected.binned= sd(pupil.base.corrected.binned, na.rm = TRUE), se.pupil.corrected.binned = sd(pupil.base.corrected.binned, na.rm = TRUE) / sqrt(length(pupil.base.corrected.binned)))%>%
  mutate(condition=fct_recode(condition, "Ball-constant"="B-C", "Ball-variable"="B-V", "Fur-constant"="F-C", "Fur-variable"="F-V"))%>%
  droplevels()

plot.animacy.pupil.trial <- ggplot(data = pupil.group.level.trial%>%filter(!is.na(condition), trial==1), aes(x = bin_low, y = mean.pupil.corrected.binned)) +
  facet_wrap(~motion)+
  ylab("Pupil size") +
  xlab("Time (in ms)") +
  geom_vline(aes(xintercept=4000), lty=1, col="darkgrey")+
   geom_vline(aes(xintercept=5000), lty=2, col="darkgrey")+
     geom_vline(aes(xintercept=6000), lty=2, col="darkgrey")+
     geom_vline(aes(xintercept=12320), lty=2, col="darkgrey")+
     geom_vline(aes(xintercept=12740), lty=2, col="darkgrey")+
       geom_vline(aes(xintercept=13990), lty=2, col="darkgrey")+
     geom_vline(aes(xintercept=14600), lty=2, col="darkgrey")+
         geom_vline(aes(xintercept=8700), lty=2, col="darkgrey")+
     geom_vline(aes(xintercept=8870), lty=2, col="darkgrey")+
   # geom_vline(aes(xintercept=6660), lty=4, col="darkgrey")+
      geom_vline(aes(xintercept=8000), lty=1, col="darkgrey")+
    geom_vline(aes(xintercept=12000), lty=1, col="darkgrey")+
      geom_vline(aes(xintercept=16000), lty=1, col="darkgrey")+
    #  geom_vline(aes(xintercept=8700), lty=2, col="darkgrey")+
     #   geom_vline(aes(xintercept=8870), lty=2, col="darkgrey")+
  geom_path(aes(x = bin_low, y = mean.pupil.corrected.binned, color = condition), alpha = 0.5, size = 0.5) +
  geom_ribbon(aes(ymin = mean.pupil.corrected.binned - se.pupil.corrected.binned, ymax = mean.pupil.corrected.binned + se.pupil.corrected.binned, fill = condition), alpha = 0.5) +
    xlim(0, 20000) +
    theme_bw()+
  scale_color_manual(values=c("darkorange", "dodgerblue", "darkgreen", "yellow"))+
  scale_fill_manual(values=c("darkorange", "dodgerblue", "darkgreen", "yellow"))+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.title = element_blank(), legend.position = c(0.8, 0.12), legend.text=element_text(size=12))


plot.animacy.pupil.trial

ggsave(plot.animacy.pupil.trial, filename = "graphics/Exp2_pupil_baseline_corrected_bytrial.png", height = 6, width = 28, scale = 0.6)
```

```{r}
save.image(file = "animacy_gamm_workspace.RData")
```


### GAMM

* Plot gaze positions
```{r}
emptyPlot(c(0,1024), c(768, 0), bty='o',
          main="Gaze positions", xlab="Xgaze", ylab="Ygaze")
points(exp.data.pupil.processed.downsampled$Xgaze, exp.data.pupil.processed.downsampled$Ygaze, pch=16, cex=.5, col=alpha(1), xpd=TRUE)
abline(h=768/2, v=1024/2, lty=1, col='white')
abline(h=768/2, v=1024/2, lty=2, col=1)
```

* Plot pupil size by subject
```{r}
par(cex=1.1)
bp <- sortBoxplot(exp.data.pupil.processed.downsampled$pupil.base.corrected.binned ~ exp.data.pupil.processed.downsampled$subject, col=alpha(1), decreasing=FALSE,
                  ylab="Pupil size", xlab="Subject", bty='n', pch=".")


```

##  GAMM

* select interest period
```{r}
dat <- exp.data.pupil.processed.downsampled%>%
  filter(bin_low >= baseline.end & bin_low <= (baseline.end+19000))%>% #select interest period
  rename(pupil_base="pupil.base.corrected.binned", time="bin_low")%>%
  arrange(subject, condition, time)%>%#order dataframe
  droplevels()
dat$motion<-as.factor(dat$motion)
dat$stimulus<-as.factor(dat$stimulus)
dat$condition<-as.factor(dat$condition)
dat$subject<-as.factor(dat$subject)
```


```{r}
dat2 <- exp.data.pupil.processed.downsampled%>%
  filter(bin_low >= (baseline.end+3000) & bin_low <= (baseline.end+7000))%>% #select interest period
  rename(pupil_base="pupil.base.corrected.binned", time="bin_low")%>%
  arrange(subject, condition, time)%>%#order dataframe
  droplevels()
dat2$motion<-as.factor(dat2$motion)
dat2$stimulus<-as.factor(dat2$stimulus)
dat2$condition<-as.factor(dat2$condition)
dat2$subject<-as.factor(dat2$subject)
```

```{r}
# Defining events (time series):
dat$Event <- interaction(dat$subject, dat$condition_trial, drop=TRUE)
dat$IsFur<- ifelse(dat$stimulus=="F",1,0)
dat$IsVariable<- ifelse(dat$motion=="V",1,0)
dat$IsFurVariable<- ifelse(dat$stimulus=="F",1,0)

m2 <- bam(pupil_base ~ condition + s(time, k=20)+ s(time, by=condition, k=20) 
          + s(Xgaze, Ygaze)
          + s(time, Event, bs='fs', m=1)
          , data=dat, discrete=TRUE, nthreads=40, method="ML")

save.image(file = "animacy_gamm_workspace.RData")

m3 <- bam(pupil_base ~  s(time, k=20)+ s(time, by=IsFur, k=20) + s(time, by=IsVariable, k=20)+ s(time, by=IsFurVariable, k=20)
          + s(Xgaze, Ygaze)
          + s(time, Event, bs='fs', m=1)
          , data=dat, discrete=TRUE, nthreads=40, method="ML")

save.image(file = "animacy_gamm_workspace3.RData")
```


```{r}
m2.null <- bam(pupil_base ~ s(time, k=20)+ 
          + s(Xgaze, Ygaze)
          + s(time, Event, bs='fs', m=1)
          , data=dat, discrete=TRUE, nthreads=40, method="ML")

save.image(file = "animacy_gamm_workspace3.RData")
#concurvity(m2, full = FALSE)
```


```{r}
summary(m2)

gam.check(m2)
acf(resid(m2), bty='n', main="ACF residuals model1")
acf(resid(m2), plot=FALSE)

compareML(m2, m2.null)
AIC(m2, m2.null)

```


```{r}
summary(m3)
gam.check(m3)
acf(resid(m3), bty='n', main="ACF residuals model1")
acf(resid(m3), plot=FALSE)

compareML(m3, m2.null)
AIC(m3, m2.null)

```




* difference curve
```{r}


plot_diff(m2, view="time", 
          comp=list(condition=c("B-C", "F-C")), rm.ranef=TRUE, main="Ball-constant - Fur-constant", 
          las=1, ylab="Est. difference in pupil size", 
            col=col2, hide.label = TRUE, plot = TRUE)#col.diff=alpha(1,f=0),v0=1800,

plot_diff(m2, view="time", 
          comp=list(condition=c("B-V", "F-V")), rm.ranef=TRUE, main="Ball-variable - Fur-variable", 
          las=1, ylab="Est. difference in pupil size", 
            col=col2, hide.label = TRUE, plot = TRUE)#col.diff=alpha(1,f=0),v0=1800,

plot_diff_nc_bs<-plot_diff(m2, view="time", 
          comp=list(condition=c("nc", "bs")), rm.ranef=TRUE, main="Disappear - Reappear", 
          las=1, ylab="Est. difference in pupil size", 
            col=col2, hide.label = TRUE, plot = FALSE)

plot_diff_nc_sb<-plot_diff(m2, view="time", 
          comp=list(condition=c("nc", "sb")), rm.ranef=TRUE, main="Disappear - Reappear", 
          las=1, ylab="Est. difference in pupil size", 
            col=col2, hide.label = TRUE, plot = FALSE)

plot_diff_bs_sb<-plot_diff(m2, view="time", 
          comp=list(condition=c("bs", "sb")), rm.ranef=TRUE, main="Disappear - Reappear", 
          las=1, ylab="Est. difference in pupil size", 
            col=col2, hide.label = TRUE, plot = FALSE)


plot_diff_m2_nc_bs<-ggplot(data=plot_diff_nc_bs, aes(x=time, y=est))+
  geom_hline(yintercept = 0)+
  geom_path(lty=2)+
  geom_ribbon(aes(x=time, ymin=est-CI, ymax=est+CI), alpha=0.2)+
  theme_bw()+
  scale_x_continuous(name="Time (in ms)", breaks=c(3000, 4000, 5000, 6000))+ ylab("Est. difference in pupil size")+ggtitle("No change - Shrinking")+
    theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

plot_diff_m2_nc_sb<-ggplot(data=plot_diff_nc_sb, aes(x=time, y=est))+
  geom_hline(yintercept = 0)+
  geom_path(lty=2)+
  geom_ribbon(aes(x=time, ymin=est-CI, ymax=est+CI), alpha=0.2)+
  theme_bw()+
  scale_x_continuous(name="Time (in ms)", breaks=c(3000, 4000, 5000, 6000))+ ylab("Est. difference in pupil size")+ggtitle("No change - Expanding")+
    theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

plot_diff_m2_bs_sb<-ggplot(data=plot_diff_bs_sb, aes(x=time, y=est))+
  geom_hline(yintercept = 0)+
  geom_path(lty=2)+
  geom_ribbon(aes(x=time, ymin=est-CI, ymax=est+CI), alpha=0.2)+
  theme_bw()+
  scale_x_continuous(name="Time (in ms)", breaks=c(3000, 4000, 5000, 6000))+ ylab("Est. difference in pupil size")+ggtitle("Shrinking - Expanding")+
    theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

library(cowplot)
pg.diff<-plot_grid(plot_diff_m2_nc_bs, plot_diff_m2_nc_sb, plot_diff_m2_bs_sb, nrow=1, labels = c("A", "B", "C"))
pg.diff
ggsave(pg.diff, filename = "graphics/plot_diff_m2_size_constancy.png", width=15, height=5, scale=0.6)



```

* plotting partial effects
```{r}
pdf("graphics/VoE_animacy_GAMM_partical_effect_m2.pdf", width=10, height=8)
plot(m2, pages = 1, all.terms = TRUE, residuals = TRUE, rug=FALSE, pch = 1, cex = 0.5, seWithMean = TRUE, shade = TRUE, shade.col = "lightblue")
dev.off()

library(mgcViz)
b <- getViz(m2)
png("graphics/VoE_animacy_GAMM_partical_effect2_m2.png", width=20, height=17, units="cm", res=300)
p1<-plot(b, allTerms = T)+theme_classic() + labs(title = NULL)
print(p1, pages = 1 )
dev.off()


#ggsave(p1, filename = "graphics/VoE_occlusion2screens_GAMM_partical_effect.png", width=10, height = 8, scale=0.8)
```


* Summed effects
```{r}

plot_smooth(m3, view="time", cond=list(IsVariable=0), rm.ranef=TRUE,
  v0=0, col=col2, lwd=2, lty=6, rug=FALSE, se=1.96,
  main="Estimated effects", ylab="Pupil (baselined)", las=1,
  ylim=c(-2000,2500))
plot_smooth(m3, view="time", cond=list(IsVariable=1), rm.ranef=TRUE,
  v0=0, col=col3, lwd=2, lty=6, rug=FALSE, add=TRUE, xpd=TRUE, se=1.96)


# legend
legend('bottomright',
       legend=c('Constant', "Variable"),
       lty=rep(c(1,6), each=2), lwd=rep(c(1,2), each=2),
       col=rep(c(col2, col3), 2), seg.len=1.5,
       bty='n', cex=.85, ncol=2, xpd=TRUE)

```

```{r}

tmp <- m2$model

plot_modelfit(m2, view="time", event=tmp$Event,n = 3)

```



```{r}
save.image(file = "Exp2_gamm_workspace.RData")
```




### Shorter interest period

```{r}
# Defining events (time series):
dat2$Event <- interaction(dat2$subject, dat2$condition_trial, drop=TRUE)
dat2$IsFur<- ifelse(dat2$stimulus=="F",1,0)
dat2$IsVariable<- ifelse(dat2$motion=="V",1,0)
dat2$IsFurVariable<- ifelse(dat2$stimulus=="F",1,0)

m4 <- bam(pupil_base ~ condition + s(time, k=20)+ s(time, by=condition, k=20) 
          + s(Xgaze, Ygaze)
          + s(time, Event, bs='fs', m=1)
          , data=dat2, discrete=TRUE, nthreads=40, method="ML")

save.image(file = "animacy_gamm_workspace4.RData")
```


```{r}
m5 <- bam(pupil_base ~  s(time, k=20)+ s(time, by=IsFur, k=20) + s(time, by=IsVariable, k=20)+ s(time, by=IsFurVariable, k=20)
          + s(Xgaze, Ygaze)
          + s(time, Event, bs='fs', m=1)
          , data=dat2, discrete=TRUE, nthreads=40, method="ML")

save.image(file = "animacy_gamm_workspace.RData")

m4.null <- bam(pupil_base ~ s(time, k=20) 
          + s(Xgaze, Ygaze)
          + s(time, Event, bs='fs', m=1)
          , data=dat2, discrete=TRUE, nthreads=40, method="ML")


save.image(file = "Exp2_gamm_workspace.RData")
```


```{r}
summary(m4)

gam.check(m4)
acf(resid(m4), bty='n', main="ACF residuals model1")
acf(resid(m4), plot=FALSE)

compareML(m4, m4.null)
AIC(m4, m4.null)

plot_diff(m4, view="time", 
          comp=list(condition=c("B-C", "B-V")), rm.ranef=TRUE, main="", 
          las=1, ylab="Est. difference in pupil size", 
            col=col2, hide.label = TRUE, plot = TRUE)#col.diff=alpha(1,f=0),v0=1800,

plot_diff(m4, view="time", 
          comp=list(condition=c("F-C", "F-V")), rm.ranef=TRUE, main="", 
          las=1, ylab="Est. difference in pupil size", 
            col=col2, hide.label = TRUE, plot = TRUE)#col.diff=alpha(1,f=0),v0=1800,
plot_diff(m4, view="time", 
          comp=list(condition=c("B-C", "F-C")), rm.ranef=TRUE, main="", 
          las=1, ylab="Est. difference in pupil size", 
            col=col2, hide.label = TRUE, plot = TRUE)#col.diff=alpha(1,f=0),v0=1800,
plot_diff(m4, view="time", 
          comp=list(condition=c("B-V", "F-V")), rm.ranef=TRUE, main="", 
          las=1, ylab="Est. difference in pupil size", 
            col=col2, hide.label = TRUE, plot = TRUE)#col.diff=alpha(1,f=0),v0=1800,
```
```{r}
summary(m5)

gam.check(m5)
acf(resid(m5), bty='n', main="ACF residuals model1")
acf(resid(m5), plot=FALSE)

compareML(m5, m4.null)
AIC(m5, m4.null)

plot_diff(m5, view="time", 
          comp=list(IsVariable=c(1,0)), rm.ranef=TRUE, main="", 
          las=1, ylab="Est. difference in pupil size", 
            col=col2, hide.label = TRUE, plot = TRUE)#col.diff=alpha(1,f=0),v0=1800,

plot_diff(m5, view="time", 
          comp=list(condition=c("F-C", "F-V")), rm.ranef=TRUE, main="", 
          las=1, ylab="Est. difference in pupil size", 
            col=col2, hide.label = TRUE, plot = TRUE)#col.diff=alpha(1,f=0),v0=1800,


```


```{r}
library(mgcViz)
b <- getViz(m4)
png("graphics/Exp2_GAMM_partical_effect2_M4.png", width=20, height=18, units="cm", res=300)
p1<-plot(b, allTerms = T)+theme_classic() + labs(title = NULL)
print(p1, pages = 1 )
dev.off()
```



### Plot gaze data
Interpolate AI values

```{r}
ai.data <- read_csv("data/ET_animacy_dynamic_IA.csv") %>%
  mutate(x_average = (x_l + x_r)/2, time.frame = start)

ai.data.constant<-ai.data%>% filter(label=="ball_IA_constant")
ai.data.variable<-ai.data%>% filter(label=="ball_IA_variable")

## interpolation
max.time <- max(ai.data.constant$end)
min.time <- min(ai.data.constant$start)
time.frame <- seq(from = min.time, to = max.time, by = 1)
xx <- as.data.frame(time.frame)

library(zoo)

ball.constant.data <- xx %>%
  full_join(ai.data.constant, by = "time.frame") %>%
  mutate(x_approx = na.approx(x_average), x_l_approx = na.approx(x_l), x_r_approx = na.approx(x_r))

## interpolation
max.time <- max(ai.data.variable$end)
min.time <- min(ai.data.variable$start)
time.frame <- seq(from = min.time, to = max.time, by = 1)
xx <- as.data.frame(time.frame)

ball.variable.data <- xx %>%
  full_join(ai.data.variable, by = "time.frame") %>%
  mutate(x_approx = na.approx(x_average), x_l_approx = na.approx(x_l), x_r_approx = na.approx(x_r))

```


```{r}
gaze_plot_data <- exp.data.pupil.processed.downsampled %>%
  filter(bin_low < 20000 ) %>%
  group_by(bin_low, condition, stimulus, motion) %>%
  summarise(mean.x = mean(Xgaze, na.rm=TRUE), median.x = median(Xgaze,  na.rm=TRUE), se.x = sd(Xgaze, na.rm=TRUE) / sqrt(length(Xgaze))) %>%
  mutate(time.frame=bin_low)%>%
   left_join(ball.constant.data%>%select(time.frame, x_l_approx, x_r_approx, x_approx)%>%rename(x_l_constant=x_l_approx, x_r_constant=x_r_approx, x_constant=x_approx))%>%
        left_join(ball.variable.data%>%select(time.frame, x_l_approx, x_r_approx, x_approx)%>%rename(x_l_variable=x_l_approx, x_r_variable=x_r_approx, x_variable=x_approx)) %>%  
  ungroup()%>%
  mutate(motion=fct_recode(as.factor(motion), "Constant"="C", "Variable"="V"), stimulus=fct_recode(as.factor(stimulus), "Fur"="F", "Ball"="B"))
```

```{r}


#gaze_plot_data$condition<-relevel(as.factor(gaze_plot_data$condition), "nc",  "bs", "sb")

con.labs <- c("Ball constant", "Ball variable", "Fur constant", "Fur variable")
names(con.labs) <- c(levels(as.factor(gaze_plot_data$condition)))



gaze_animacy_plot<-ggplot(data = gaze_plot_data%>%filter(!is.na(condition)), aes(x = time.frame, y = mean.x)) +
     # facet_wrap(~condition,labeller=labeller(condition=con.labs)) +
  facet_grid(motion~stimulus)+
  #moving ball:
  geom_ribbon(data = gaze_plot_data %>% filter(motion=="Constant"), aes(x = time.frame, ymin = x_l_constant, ymax = x_r_constant), fill = "#988B2D", alpha = 0.8) +
    geom_ribbon(data = gaze_plot_data %>% filter(motion=="Variable"), aes(x = time.frame, ymin = x_l_variable, ymax = x_r_variable), fill = "#988B2D", alpha = 0.8) +
# gaze data:
    geom_point(alpha = 0.1, size=0.5) +
  geom_path(aes(y = median.x), size = 1.2) +
   geom_ribbon(aes(ymin = mean.x - se.x, ymax = mean.x + se.x), alpha = 0.5)+
  ylab("Horizontal coordinates (in px)") +
  xlab("Time (in ms)") +
    theme_bw()+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        strip.text.x = element_text(size = 12),
        strip.text.y = element_text(size = 12))

gaze_animacy_plot
ggsave(gaze_animacy_plot,filename="graphics/animacy_mean_x_gaze.png", height = 5, width = 8, scale = 0.7)
```


### Adding screenshots

```{r}
library(cowplot)
ball_photo <- "screenshots/animacy_constant_motion_ball.mkv_snapshot_00.02.000.jpg"
fur_photo <- "screenshots/animacy_constant_motion_fur.mkv_snapshot_00.02.000.jpg"


ball_photo <- ggdraw(theme(plot.margin = unit(c(0, 0, 0, 0), "cm"))) + draw_image(ball_photo)
fur_photo <- ggdraw(theme(plot.margin = unit(c(0, 0, 0,0), "cm"))) + draw_image(fur_photo)

animacy_pics<-plot_grid(ball_photo, fur_photo, nrow=1)

```

```{r}
pg.animacy1<-plot_grid(gaze_animacy_plot, plot.animacy.pupil , ncol=1, nrow=2, rel_heights = c(1.0, 1.0), labels = c("B", "C"))


pg.animacy<-plot_grid(animacy_pics, pg.animacy1 , ncol=1, nrow=2, rel_heights = c(0.75, 2), labels = c("A", "", ""), label_colour = "white")

pg.animacy

ggsave(pg.animacy, filename = "graphics/ET_VoE_animcy_plotgrid.png", width = 9, height=12, scale=0.75)
ggsave(pg.animacy, filename = "graphics/ET_VoE_animcy_plotgrid.pdf", width = 9, height=14, scale=0.75)
```



## Dynamic AoI analysis: r-squared


```{r}
dynamic.aoi.data <- sample.data %>%
  filter(time.frame < 16000) %>%
  group_by(condition, time.frame, subject) %>%
  summarise(mean.x = mean(RIGHT_GAZE_X_no_blinks), mean.y = mean(RIGHT_GAZE_Y)) %>%
     left_join(ball.constant.data%>%select(time.frame,x_approx)%>%rename(x_constant=x_approx))%>%
        left_join(ball.variable.data%>%select(time.frame,  x_approx)%>%rename( x_variable=x_approx))


dynamic.aoi.data$condition<-as.factor(dynamic.aoi.data$condition)
levels(dynamic.aoi.data$condition)


```


```{r}
library(broom)

r2.constant <- dynamic.aoi.data %>%
  filter(time.frame < 16000 & time.frame > 500 & (condition=="B-C" | condition=="F-C")) %>% #ip until the ball stops
  droplevels() %>%
  nest(-subject, -condition) %>%
  mutate(
    fit = map(data, ~ lm(mean.x ~ x_constant, data = .)),
    results = map(fit, glance)
  ) %>%
  unnest(results) %>%
  select(subject, condition, r.squared) %>%
  rename(r.sq.exp = r.squared) %>%
  mutate(across(where(is.numeric), round, 3))

r2.variable <- dynamic.aoi.data %>%
  filter(time.frame < 16000 & time.frame > 500 & (condition=="B-V" | condition=="F-V")) %>% #ip until the ball disappeared
  droplevels() %>%
  nest(-subject, -condition) %>%
  mutate(
    fit = map(data, ~ lm(mean.x ~ x_variable, data = .)),
    results = map(fit, glance)
  ) %>%
  unnest(results) %>%
  select(subject, condition, r.squared) %>%
  rename(r.sq.exp = r.squared) %>%
  mutate(across(where(is.numeric), round, 3))

r2.constant %>%
  group_by(condition) %>%
  summarise(mean = mean(r.sq.exp), se = sd(r.sq.exp)/length(r.sq.exp),median = median(r.sq.exp), min = min(r.sq.exp), max = max(r.sq.exp), sd = sd(r.sq.exp))

r2.variable %>%
  group_by(condition) %>%
  summarise(mean = mean(r.sq.exp), se = sd(r.sq.exp)/length(r.sq.exp), median = median(r.sq.exp), min = min(r.sq.exp), max = max(r.sq.exp), sd = sd(r.sq.exp))

```



## Trial report analysis

* Read Data

```{r}
trial.data<-read.csv(file="data/Exp2_Trial_report_anonymised.csv")
```




* descriptives
```{r}
trial.data.ind<-trial.data%>%
  group_by(condition, subject)%>%
  summarise(fix_duration=mean(AVERAGE_FIXATION_DURATION), sacc_amplitude=mean(AVERAGE_SACCADE_AMPLITUDE), fix_count=mean(	FIXATION_COUNT), max_pupil_size=mean(PUPIL_SIZE_MAX), sacc_count=mean(SACCADE_COUNT))%>%
ungroup()

trial.data.ind.motion<-trial.data%>%
  group_by(motion, subject)%>%
  summarise(fix_duration=mean(AVERAGE_FIXATION_DURATION), sacc_amplitude=mean(AVERAGE_SACCADE_AMPLITUDE), fix_count=mean(	FIXATION_COUNT), max_pupil_size=mean(PUPIL_SIZE_MAX), sacc_count=mean(SACCADE_COUNT))%>%
ungroup()

trial.data.ind.stimulus<-trial.data%>%
  group_by(stimulus, subject)%>%
  summarise(fix_duration=mean(AVERAGE_FIXATION_DURATION), sacc_amplitude=mean(AVERAGE_SACCADE_AMPLITUDE), fix_count=mean(	FIXATION_COUNT), max_pupil_size=mean(PUPIL_SIZE_MAX), sacc_count=mean(SACCADE_COUNT))%>%
ungroup()

trial_descriptives<-trial.data.ind%>%
  group_by(condition)%>%
  summarise(mean_fix_duration=mean(fix_duration), se_fix_duration=sd(fix_duration)/length(fix_duration), mean_fix_count=mean(fix_count), se_fix_count=sd(fix_count)/length(fix_count), mean_sacc_amplitude=mean(sacc_amplitude), se_sacc_amplitude=sd(sacc_amplitude)/length(sacc_amplitude), mean_sacc_count=mean(sacc_count),se_sacc_count=sd(sacc_count)/length(sacc_count), n=length(sacc_count))

write.csv(trial_descriptives, file = "saves/trial_descriptives_exp2.csv")

```
* motion comparison
```{r}



library(broom)

x1<-trial.data.ind.motion%>%
  summarise(ttest_fix_duration = list(t.test(fix_duration ~ motion, paired=TRUE)))%>%
  mutate(ttest_fix_duration = map(ttest_fix_duration, tidy)) %>%
  unnest()


x2<-trial.data.ind.motion%>%
  summarise(ttest = list(t.test(fix_count ~ motion, paired=TRUE)))%>%
  mutate(ttest = map(ttest, tidy)) %>%
  unnest()

x3<-trial.data.ind.motion%>%
  summarise(ttest = list(t.test(sacc_amplitude ~ motion, paired=TRUE)))%>%
  mutate(ttest = map(ttest, tidy)) %>%
  unnest()

x4<-trial.data.ind.motion%>%
  summarise(ttest = list(t.test(sacc_count ~ motion, paired=TRUE)))%>%
  mutate(ttest = map(ttest, tidy)) %>%
  unnest()
rowname<-c("fix_duration", "fix_count", "sacc_amp", "sacc_count")
xx<-cbind(rowname,rbind(x1,x2, x3,x4))
write.csv(xx, file = "saves/trial_ttest_exp2_motion.csv")

```
* stimulus comparison
```{r}



library(broom)

x1<-trial.data.ind.stimulus%>%
  summarise(ttest_fix_duration = list(t.test(fix_duration ~ stimulus, paired=TRUE)))%>%
  mutate(ttest_fix_duration = map(ttest_fix_duration, tidy)) %>%
  unnest()


x2<-trial.data.ind.stimulus%>%
  summarise(ttest = list(t.test(fix_count ~ stimulus, paired=TRUE)))%>%
  mutate(ttest = map(ttest, tidy)) %>%
  unnest()

x3<-trial.data.ind.stimulus%>%
  summarise(ttest = list(t.test(sacc_amplitude ~ stimulus, paired=TRUE)))%>%
  mutate(ttest = map(ttest, tidy)) %>%
  unnest()

x4<-trial.data.ind.stimulus%>%
  summarise(ttest = list(t.test(sacc_count ~ stimulus, paired=TRUE)))%>%
  mutate(ttest = map(ttest, tidy)) %>%
  unnest()
rowname<-c("fix_duration", "fix_count", "sacc_amp", "sacc_count")
xx<-cbind(rowname,rbind(x1,x2, x3,x4))
write.csv(xx, file = "saves/trial_ttest_exp2_stimulus.csv")

```

## Dwell time analysis


Read Data

```{r}
end.ip.data<-read.csv(file="data/Exp2_IA_report_anonymised.csv")
```

GLMM
```{r}
library(glmmTMB)
```
+preprocessing of data for model
```{r}
model.data<-end.ip.data%>%filter(IP_DURATION>0)

model.data$z.trial<-scale(model.data$trial, center = TRUE, scale=TRUE)
model.data$motion<- as.factor(model.data$motion)
model.data$motion.c<- as.numeric(model.data$motion)-mean(as.numeric(model.data$motion))
model.data$stimulus<- as.factor(model.data$stimulus)
model.data$stimulus.c<- as.numeric(model.data$stimulus)-mean(as.numeric(model.data$stimulus))
model.data$prop.dwell.time<-model.data$IA_DWELL_TIME/model.data$IP_DURATION
hist((model.data$prop.dwell.time))
hist((log(model.data$IA_DWELL_TIME+1)))


model.data$prop.dwell.time.scaled <- (model.data$prop.dwell.time*(length(model.data$prop.dwell.time) - 1) + 0.5)/length(model.data$prop.dwell.time)#transform DV to exclude 0 and 1s
hist((model.data$prop.dwell.time.scaled))

```
+ fitting model
```{r}
m1.end.ip<-glmmTMB(prop.dwell.time.scaled ~ motion*stimulus + z.trial + (1+motion.c+stimulus.c+z.trial||subject), family=beta_family, data=model.data,  control=glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000)))


overdisp.test(m1.end.ip)
summary(m1.end.ip)
```


```{r}
drop1(m1.end.ip, test="Chisq")

```

* removing nonsignificant interaction


```{r}

m2.end.ip<-glmmTMB(prop.dwell.time.scaled ~ motion+stimulus + z.trial + (1+motion.c+stimulus.c+z.trial||subject), family=beta_family, data=model.data,  control=glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000)))


overdisp.test(m2.end.ip)
summary(m2.end.ip)
```
```{r}
drop1(m2.end.ip, test="Chisq")
```

* Collinearity

```{r}
library(car)
xx=lm(prop.dwell.time.scaled ~ motion+stimulus + z.trial, data=model.data)
vif(xx)
```

